\begin{thebibliography}{999}
\addcontentsline{toc}{chapter}{\numberline{}References}



\bibitem{bib1}
	Laura Ruotsalainen , Aiden Morrison, Maija Mäkelä , Jesperi Rantanen , and Nadezda Sokolova  “Improving Computer Vision-Based Perception for Collaborative Indoor Navigation”, IEEE Sensors, Vol.: 22, Issue: 6, p:4816 – 4826, Aug 2021.
\bibitem{bib2}
	Dawar Khan, Zhanglin Cheng, Hideaki Uchiyama, Sikandar Ali, Muhammad Asshad, Kiyoshi Kiyokawa “Recent advances in vision-based indoor navigation: A systematic literature review”, ScienceDirect Computers & Graphics, Vol,: 104, P: 24-45, May 2022

\bibitem{bib3}
	Fallah N, Apostolopoulos I, Bekris K, Folmer E.,” Indoor human navigation systems: a survey.” Interact Comput. 2013;25(1):21–33.



\bibitem{bib4}
Tian Y, Yang X, Arditi A., “Computer vision-based door detection for accessibility of unfamiliar environments to blind persons.”, In: International conference on computers for handicapped persons. Berlin: Springer, 2010, p. 263–70.


\bibitem{bib5}
Bay, H., Tuytelaars, T., Van Gool, L. (2006), “SURF: Speeded Up Robust Features”, In: Leonardis, A., Bischof, H., Pinz, A. (eds) Computer Vision – ECCV 2006. ECCV 2006. Lecture Notes in Computer Science, vol 3951.

\bibitem{bib6}
	L. Ruotsalainen, M. Kirkko-Jaakkola, J. Rantanen, and M. Mäkelä,
“Error modelling for multi-sensor measurements in infrastructure-free
indoor navigation,” Sensors, vol. 18, no. 2, p. 590, Feb. 2018.
\bibitem{bib7}
A. Ali and N. El-Sheimy, “Low-cost MEMS-based pedestrian navigation
technique for GPS-denied areas,” J. Sensors, vol. 2013, pp. 1–10,
Jul. 2013, doi: 10.1155/2013/197090.
\bibitem{bib8}
	I. Pires, N. Garcia, N. Pombo, and F. Flórez-Revuelta, “From data
acquisition to data fusion: A comprehensive review and a roadmap
for the identification of activities of daily living using mobile devices,”
Sensors, vol. 16, no. 2, p. 184, Feb. 2016, doi: 10.3390/s16020184
\bibitem{bib9}
A. J. Morrison, L. Ruotsalainen, M. Makela, J. Rantanen, and
N. Sokolova, “Combining visual, pedestrian, and collaborative naviga-
tion techniques for team based infrastructure free indoor navigation,”
in Proc. 32nd Int. Tech. Meeting Satell. Division Inst. Navigat. (ION
GNSS+), Oct. 2019, pp. 2692–2701.
\bibitem{bib10}
J.-O. Nilsson, J. Rantakokko, P. Handel, I. Skog, M. Ohlsson,
and K. V. S. Hari, “Accurate indoor positioning of firefighters using
dual foot-mounted inertial sensors and inter-agent ranging,” in Proc.
IEEE/ION Position, Location Navigat. Symp. (PLANS), May 2014,
pp. 631–636.
\bibitem{bib11}
K. Abdulrahim, T. Moore, C. Hide, and C. Hill, “Understanding the
performance of zero velocity updates in MEMS-based pedestrian navi-
gation,” Int. J. Advancements Technol., vol. 5, no. 2, pp. 1–8, 2014.
\bibitem{bib12}
J. Zhang, M. Ren, P. Wang, J. Meng, and Y. Mu, “Indoor localization
based on VIO system and three-dimensional map matching,” Sensors,
vol. 20, no. 10, p. 2790, May 2020.
\bibitem{bib13}
F. Bonin-Font, A. Ortiz, and G. Oliver, “Visual navigation for mobile
robots: A survey,” J. Intell. Robotic Syst., vol. 53, no. 3, pp. 263–296,
Nov. 2008, doi: 10.1007/s10846-008-9235-4.
\bibitem{bib14}
N. W. Campbell, M. R. Pout, M. D. J. Priestly, E. L. Dagless,
and B. T. Thomas, “Autonomous road vehicle navigation,” Eng. Appl.
Artif. Intell., vol. 7, no. 2, pp. 177–190, 1994, doi: 10.1016/0952-
1976(94)90022-1.
\bibitem{bib15}
J. Xu et al., “Edge assisted mobile semantic visual SLAM,” in Proc.
IEEE INFOCOM Conf. Comput. Commun., Jul. 2020, pp. 1828–1837.
\bibitem{bib16}
 H. Bay, A. Ess, T. Tuytelaars, and L. Van Gool, “Speeded-up robust
features (SURF),” Comput. Vis. Image Understand., vol. 110, no. 3,
pp. 346–359, 2008, doi: 10.1016/j.cviu.2007.09.014
\end{thebibliography}




